### 2020-01-18 cv_models.tex
updated DenseNet
cv table added
comments add for mike

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & & & & & \\
 ResNet & & & & & \\
 ResNet-1K & & & & & \\
 DenseNet & & & &  &\\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}

@@

    \subfigure[ VGG ]{
        \includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet ]{
        \includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.5cm]{img/DenseNet_all_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{Power law exponent $\alpha$ vs layer for VGG, ResNet, and DenseNet models}
    \label{fig:vgg-alpha-layers}
\end{figure}

>>>>

\michael{We set up the methdology we will use later, and give examples on the CV models
and explain how to interpret things a bit. We study pretrained CV models.
We look at correlation with the reportest test accuarcies.
 We will run linear regressions. We will compute the RMSE.  
We study alpha and the 4 norms.  we could add softrank with some work.

We introduce the notion of Correlation Flow and 
tell a nice story about residual connections
with VGG RseNet and DenseNet}

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & 6 & 0.56 & 0.53 & 0.48 & 0.42  \\
 ResNet & 5 & 0.9 & 1.4 & 0.61 & 0.66  \\
 ResNet-1K & 19 & 2.4 & 3.6 & 1.8 & 1.9  \\
 DenseNet & 4 & 0.3 & 0.26 & 0.16 & 0.21 \\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}

DISCUSS TABLE

@@

    \subfigure[ VGG ]{
        \includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet ]{
        \includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.5cm]{img/DenseNet_fnl_alpha_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{Power law exponent $\alpha$ vs layer for VGG, ResNet, and DenseNet models}
    \label{fig:vgg-alpha-layers}
\end{figure}

### 2020-01-18 nlp_models.tex
comments add for mike

[THESE RESULTS HAVE TO BE REDONE BY REMOVING THE FIRST LAYER...]

>>>>

\michael{We show that this not only works for CV, so we look at NLP.
We now look in detail at the alpha metric, the spectral norm, and the new norm.
We compare good and bad models, and a series of increasingly big models
trained on big data sets.  We show why alpha works but spectral norm is not enough

}
